# Missing values

Missing data would substantially affect the precision of the analysis and could lead to wrong prediction as well as conclusion. In this chapter, we examined the missing data in the two data sets. However, after data cleaning and transformation, there is no missing value in the hate crime data set. Consequently, we mainly focused on the missing values in the index crime data set. 


```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(knitr)
library(lubridate)
library(readr)
library(patchwork)
library(naniar)
NYPD <- read_csv("data/NYPD.csv")
```

```{r}
library(patchwork)
library(tidyverse)
createNAplot <- function(data, percent = TRUE) {
  #find missing patterns
  missing_patterns <- data.frame(is.na(data)) %>%
  group_by_all() %>%
  count(name = "Total", sort = TRUE) %>%
  ungroup() 
  
  # prepare the data
  if (percent == TRUE) { 
    missing_patterns <- missing_patterns %>%
      mutate(Total = (Total / sum(Total)) *100) 
  }
  
  mp1 <- missing_patterns %>%
  mutate(complete = ifelse(rowSums(.[1:ncol(missing_patterns)-1]) == 0, TRUE, FALSE))%>%
  rownames_to_column("missing_pattern")
  
  mp2 <-  mp1%>%
  gather(key, value, -missing_pattern, -Total, -complete) %>%
  mutate(Disappearences = ifelse(value == TRUE, Total, 0))
    
  mp2$missing_pattern <- as.factor(mp2$missing_pattern)
  
  # plot missing values by variable
  p1 <- mp2 %>%
  group_by(key) %>%
  summarize(freq = sum(Disappearences)) %>%
  ggplot(aes(x = fct_reorder(key, freq, .desc = TRUE), y=freq)) +
  geom_col(fill = "cornflowerblue", alpha = 0.7) +
  ggtitle("Missing Value Pattern") +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank(),panel.grid.minor.x = element_blank())+
  xlab(NULL)+
  theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
  if (percent == TRUE){
    p1 <- p1 +  ylab(expression(paste("% rows \n missing:"))) 
  } else { p1 <- p1 +  ylab(expression(paste("num rows \n missing:"))) }
  
  # plot missing values by pattern
  p2 <- ggplot(mp1, aes(y = fct_rev(missing_pattern), x = Total, alpha = complete)) +
  geom_col(fill = 'cornflowerblue') +
  scale_alpha_manual(values = c(0.7,1), limits = c(FALSE,TRUE)) +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank())+
  theme(legend.position="none")+
    theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))+
  ylab(NULL)+
  scale_x_continuous(breaks = c(0,100000,200000,300000,400000),labels = c(0,"100K","200K","300K","400K"))
  if (percent == TRUE){
    p2 <- p2 +  xlab("% rows") 
  } else { p2 <- p2 + xlab("row count") }
  
  # plot main plot
  xpos <- levels(fct_reorder(mp2$key, -mp2$Disappearences, sum))[ncol(missing_patterns)/2]
  ypos <- mp2 %>%
    filter(complete == TRUE) %>%
    select(missing_pattern) %>%
    distinct(.) %>%
    simplify(.)
  
  p3 <- ggplot(mp2, aes(x = fct_reorder(key, -Disappearences, sum), y = fct_rev(missing_pattern), fill = value, alpha = complete)) +
  geom_tile(color = "white") +
  scale_fill_manual(values = c("grey", "mediumpurple")) +
  scale_alpha_manual(values = c(0.7, 1),limits=c(FALSE,TRUE)) +
  theme_classic() +
  theme(legend.position="none")+
  xlab(NULL) +
  ylab("missing pattern")+
  annotate("text", x= xpos, y=ypos, label = "complete case")+
  theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
  
 # assemble plots
  patchwork <- p1 + plot_spacer() + p3 + p2 + 
  plot_layout(widths = c(3, 1), heights = c(1, 3))

  patchwork 

}
```

```{r missing_pattern}
createNAplot(NYPD,FALSE)
```

From the plot above, it is recognizable that most cases are complete, with no missing value. *Location*, *County* and *Offense* are the three most apparent missing features among 10. They have 1,104, 463 and 5 missing rows respectively. We took a further step to analyze the significance of these missing variables and presented it in the following plot. 
\
\

```{r perform_missing, fig.width=5,fig.height=3.5}
gg_miss_var(NYPD, show_pct = TRUE) + ggtitle("The Percentage of Missing Rows") + xlab("Percentage")
```


In this large data set containing over 40K rows, the percentages of missing *Location* and *County* rows are both less than 0.3%, and *offense* is not even noticeable. In this way, we concluded that the existence of missing values in this data set does not have significant statistical power of producing biased results.
